Networks Matter in International Relations:\\A Latent Network Approach to Analysis

### 2017-10-21 paper/4_app.tex
cleanup, coefs left, waiting on rose out

We obtained the data for each of these studies from their replication archives and replicated the main results of each of the articles.\footnote{Without exception this was straightforward to accomplish, thanks to an increasing norm in the social sciences of open data sharing.} We also examine each of the models using the AME framework described above.  Our goal is to ascertain whether the ignored interdependencies---the non-iid structure of the relational data---would result in different model estimates when they were addressed in an AME framework, and more importantly to see if there were substantive opportunities that were presented with the dynamic factor approach.  
Finally, in each study we assess whether there is any new substantive finding that emerges or indeed if any disappear once the interdependencies in the data are modeled.

@@

Given current practices, most scholars have a single variable in a complicated empirical model that they look at for evaluating the validity of their empirically estimated models.  Whether putative control variables, for example, are precisely estimated is less important. Generally, interpretations focus on a small set of independent variables.  In the study by Reiter and Stam (2003) the main question is to determine in mixed dyads---consisting of a democratic country and country ruled by a personalist dictatorship---whether it is the
democratic country or the personalist country that is associated with a greater likelihood that the dyad is in a dispute.  In a regression including fourteen coefficients, they focus on whether the variables that capture whether the initiator is a democratic country are statistically significant.\footnote{In particular, the variables \texttt{Pers/Democ} and \texttt{Democ/Pers} in Model 3, in Table 1, page 335.} In our evaluation we focus on the same question in the re-examination of the Reiter and Stam study to determine whether the model replicates when re-estimated within the AME framework. Each of the other four studies also has a crucial finding that we hone in on to further draw into focus the potential differences brought about by utilizing an AME estimation procedure.  In Table~\ref{tab:modelFindingSumm}, we present the overall results; the term \textit{does not replicate} indicates only that the sign and/or significance of the putatively crucial finding in the original study is not also found in the AME estimation.

@@

We utilize three performance criteria to compare the models: Receiver Operator Characteristic (ROC) curves, Precision Recall (PR) curves, and separation plots. ROC curves look at the trade-off between true positive rates and false positive rates at different thresholds of classification. An issue with an ROC Curve when looking at conflict, is that it is relatively rare at the dyadic level: in most years only 3\% of possible dyads are in conflict with one another. If peace is common, even a poor model will have a very low False Positive Rate. The ROC curves are best for balanced samples with as many events as non-events. To better assess which models predict the presence of conflict, not just its absence, we look at PR Curves. These examine the trade-offs between the percentage of conflicts a model predicts, and the percentage of predicted conflicts which occur. Lastly, we examine separation plots \citep{greenhill:etal:2011}. These provide an intuitive visualization of the accuracy of our predictions by juxtaposing a line showing the predicted probability of conflict with whether conflict actually occurs for all cases (where the cases are sorted by the predicted probability and then colored to indicate the outcome). Here a perfect model would have all cases where conflict actually exists on the right with a predicted probability of $1$, and would predict $0$ in all other cases. All of the models' performance out of sample by these metrics are displayed in figure \ref{fig:roc_ame}. The AME model with covariates is the best performing model out of sample in all cases. This model outperforms each of the GLM variants by a notable margin.
% % % % % % % % % % % % % % % % % %

@@

%\begin{figure}
%%\includegraphics[width=\textwidth]{reiter_coefs_all.pdf}
%\caption{\label{fig:reitCoef} Coefficient plot of Reiter \& Stam (2003)'s original model (blue) compared to AME model (red). }
%\end{figure}

\begin{figure}
\centering   
\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=65mm]{reiter_auc_outsamp.pdf}}
\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{reiter_pr_outsamp.pdf}}
\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

@@

% TO DO: include discussion and analysis of different K's in appendix (for M cD)
%\begin{figure}
%%\includegraphics[width=\textwidth]{McDonald_coefs.pdf}
%\caption{\label{fig:mcdCoefs}Coefficient plot of McDonald (2004)'s original model (blue) compared to AME model (red).}
%\end{figure}
%\FloatBarrier
%\begin{figure}
%\centering   
%\subfigure[AUC]{\label{fig:mcDauc}\includegraphics[width=65mm]{McDonald_auc_outsamp.pdf}}
%\subfigure[Precision and Recall]{\label{fig:mcDpr}\includegraphics[width=65mm]{McDonald_pr_outsamp.pdf}}
%\caption{\label{fig:mcdall} Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
%\end{figure}

Our re-estimation with AME reveals that trade relations are highly interdependent and exhibit important patterns of transitivity.  Or, in other words, if countries $i$ and $j$ are highly dependent and countries $j$ and $k$ are also highly dependent, then we are likely to observe high dependency between countries $i$ and $k$. Our findings support those of Traag and Lupu (2013) which argue that indirect trade relations reduce the probability of conflict. This indicates that conflict is less likely between members of a trade community. Once we control for these dependencies, we can more clearly interpret the positive link between trade and conflict.  The most striking thing is that AME finds a positive conditional association between trade dependence and conflict ($\hat{\beta}= 18.4, \quad \sigma_{\hat{\beta}} = 28.6$), while the comparable numbers for the logistic regression found in the original articles are negative ($\hat{\beta}= -22.2, \quad \sigma_{\hat{\beta}} = 15.2$). 
%The AME coefficient is not only in the opposite direction, but it is approximately three times more precisely estimated.  
At the same time, the AME has ROC and PR curves (shown in the Appendix) that dominate the results found in McDonald (2004).

@@

In 2004, Andrew Rose published a study in the \textit{American Economic Review} \nocite{rose:2004} that proved to be quite controversial in terms of macroeconomic trade theory and in terms of trade policy in a variety of nations. It also provoked a number of responses in the international political economy literature \cite{tomz:etal:2007,ward:etal:2013}.  Rose's basic argument is that despite longstanding arguments made by trade theorists and the World Trade Organization that WTO membership fosters greater cooperation and thereby more trade among its members, the empirics do not bear out such claims. He uses a standard gravity model with dyadic data on bilateral merchandise trade (not services) for $175$ countries over a period of five decades. Estimating this model using OLS within many differing contexts, his conclusion was that: ``An extensive search reveals little evidence that countries joining or belonging to the GATT/WTO have different trade patters from outsiders... (2004, page 98, abstract).''  The data for this study have been widely used in replications by many searching for the missing effects of the WTO---as well as preferential trade agreements, bilateral investment theories, and other aspects of modern trade theory.

When we compare the results of Rose's original OLS model to the AME model accounting for network dependencies, the results are generally similar. The main result of the model---the null effect of membership in the WTO, as represented by the ``One-In" and ``Both-In" variables---persists in the AME model. However, while in the original model there was a clear positive relationship between Real GDP and Trade, most of this effect vanishes in the AME model. The random effects shown in Figure~\ref{fig:roser} reveal the cause of much of this divergence. Here, the states with the most positive random effects are also states with high GDP, though not necessarily high GDP/capita.\footnote{Note: Qatar exhibits strongly negative random effects.} Thus, the effect of GDP in the original model was, in part, an artifact of first-order dependencies. Most of the other results of the model are constant across each model, though some geographic features, such as islands and landlocked states, have a more clear effect on trade once we account for these network dependencies. When we account for network interdependencies, we observe a markedly lower Root Mean Squared Error out-of-sample---$3.23$ for the OLS model and $1.77$ for the AME model. While the basic model replicates with the basic result, there are substantial and substantive improvements gleaned from the AME results.

@@

We re-estimated model 6 from Table 6 (2017, 34). The results are presented in Figure~\ref{fig:giberrepl} in order to facilitate explicit comparison.
The results obtained with \texttt{amen} stand in stark contrast to those found with a logistic regression (with dyad clustered, robust standard errors).  Most importantly, the primary variable from the Gibler study, parity of the members of a dyad at the year in which they entered the international system, is shown to be unimportant in the AME results.  Not only is the value of this parameter small, but it has a very large relative standard error---over a magnitude larger than the parameter itself ($z= 0.038$). In addition, the variable indicating whether both members of the dyad were coded as democracies (joint democracy) follows the same pattern: important and strong in the logistic results, but this disappears once interdependencies are modeled.  As might be expected, the strong geographic clustering in the original study is about one-quarter as strong in the AME estimations. Similarly, rivalry coefficients are about one-third the size in the AME formulation, but a great deal more precisely measured ($z=18.116$).

We utilized the original and the AME results from Gibler's model 6 in Table 6 to calculate the expected values for one scenario. We focused on the variables measuring rivalry.  We used mean or modal values for all independent variables, except we changed the rivalry variable to indicate that there was a rivalry when the actual data suggest there is none.  The expected values of this scenario are essentially a first difference plot comparing results with the model when estimated in two different ways: Gibler's GLM estimation and our AME approach.  As this Figure~\ref{fig:gibmargeff} illustrates, the AME results differ from the GLM in two distinct ways. First, the expected value of the dependent variable---the probability of the onset of a militarized interstate dispute, is considerably higher when taking interdependencies into account with the AME model.  These are rare events, so the probabilities are low, but the difference is a factor of $3x$. Thus, you get quite substantially different expected values from these two models.  Second, the GLM model has a standard errors which underestimate the true variability, in part because some of them are assumed to be zero.  This shows up in the narrow density of predicted outcomes for the GLM model, compared to the density seen with the AME. The latter reflects a wider range of potential outcomes, reflecting the incorporation of uncertainty in the AME model.

@@

First and foremost, many  findings which emerge from models that do not take interdependencies into account lose their statistical significance when network effects are estimated via AME. This should not be news---since the finding has long been in the theoretical literature, but given the state of current literature in international relations is still pertinent.  Not only
are coefficients biased in the OLS and logit approaches to the analysis of dyadic data, but they are often imprecisely measured, with inflated standard errors.  This means that significant testing (for better or worse) is compromised when network effects are ignored.

@@

Third, it is evident that the actual results---not the estimated coefficents and their covariances---which are generated by the models differ greatly in expectations.  This implies that policy experimentations with the models, as well as scenario-based simulations and forecasting of GLM models are likely to often give misleading results compared to the AME approach.

>>>>

We obtained the data for each of these studies from their replication archives and replicated the main results of each of the articles.\footnote{Without exception this was straightforward to accomplish, thanks to an increasing norm in the social sciences of open data sharing.} We also examine each of the models using the AME framework described above.  Our goal is to ascertain whether the ignored interdependencies -- the non-iid structure of the relational data -- would result in different model estimates when they were addressed in an AME framework, and more importantly to see if there were substantive opportunities that were presented with the dynamic factor approach.  
Finally, in each study we assess whether there is any new substantive finding that emerges or indeed if any disappear once the interdependencies in the data are modeled.

@@

Given current practices, most scholars have a single variable in a complicated empirical model that they look at for evaluating the validity of their empirically estimated models.  Whether putative control variables, for example, are precisely estimated is less important. Generally, interpretations focus on a small set of independent variables.  In the study by Reiter and Stam (2003) the main question is to determine in mixed dyads -- consisting of a democratic country and country ruled by a personalist dictatorship -- whether it is the democratic country or the personalist country that is associated with a greater likelihood that the dyad is in a dispute.  In a regression including fourteen coefficients, they focus on whether the variables that capture whether the initiator is a democratic country are statistically significant.\footnote{In particular, the variables \texttt{Pers/Democ} and \texttt{Democ/Pers} in Model 3, in Table 1, page 335.} In our evaluation we focus on the same question in the re-examination of the Reiter and Stam study to determine whether the model replicates when re-estimated within the AME framework. Each of the other four studies also has a crucial finding that we hone in on to further draw into focus the potential differences brought about by utilizing an AME estimation procedure.  In Table~\ref{tab:modelFindingSumm}, we present the overall results; the term \textit{does not replicate} indicates only that the sign and/or significance of the putatively crucial finding in the original study is not also found in the AME estimation.

@@

We utilize three performance criteria to compare the models: Receiver Operator Characteristic (ROC) curves, Precision Recall (PR) curves, and separation plots. ROC curves look at the trade-off between true positive rates and false positive rates at different thresholds of classification. An issue with an ROC Curve when looking at conflict, is that it is relatively rare at the dyadic level: in most years only 3\% of possible dyads are in conflict with one another. If peace is common, even a poor model will have a very low False Positive Rate. The ROC curves are best for balanced samples with as many events as non-events. To better assess which models predict the presence of conflict, not just its absence, we look at PR Curves. These examine the trade-offs between the percentage of conflicts a model predicts, and the percentage of predicted conflicts which occur. Lastly, we examine separation plots \citep{greenhill:etal:2011}. These provide an intuitive visualization of the accuracy of our predictions by juxtaposing a line showing the predicted probability of conflict with whether conflict actually occurs for all cases (where the cases are sorted by the predicted probability and then colored to indicate the outcome). Here a perfect model would have all cases where conflict actually exists on the right with a predicted probability of $1$, and would predict $0$ in all other cases. All of the models' performance out of sample by these metrics are displayed in figure \ref{fig:roc_ame}. The AME model with covariates is the best performing model out of sample in all cases. This model outperforms each of the GLM variants by a notable margin.

@@

\begin{figure}
	\centering   
	\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=.45\textwidth]{reiter_stam_roc_outSample.pdf}}
	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=.45\textwidth]{reiter_stam_pr_outSample.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

@@

% TO DO: include discussion and analysis of different K's in appendix (for M cD)

Our re-estimation with AME reveals that trade relations are highly interdependent and exhibit important patterns of transitivity.  Or, in other words, if countries $i$ and $j$ are highly dependent and countries $j$ and $k$ are also highly dependent, then we are likely to observe high dependency between countries $i$ and $k$. Our findings support those of Traag and Lupu (2013) which argue that indirect trade relations reduce the probability of conflict. This indicates that conflict is less likely between members of a trade community. Once we control for these dependencies, we can more clearly interpret the positive link between trade and conflict.  The most striking thing is that AME finds a positive conditional association between trade dependence and conflict ($\hat{\beta}= 18.4, \quad \sigma_{\hat{\beta}} = 28.6$), while the comparable numbers for the logistic regression found in the original articles are negative ($\hat{\beta}= -22.2, \quad \sigma_{\hat{\beta}} = 15.2$). At the same time, the AME has ROC and PR curves (shown in the Appendix) that dominate the results found in McDonald (2004).

@@

In 2004, Andrew Rose published a study in the \textit{American Economic Review} \nocite{rose:2004} that proved to be quite controversial in terms of macroeconomic trade theory and in terms of trade policy in a variety of nations. It also provoked a number of responses in the international political economy literature \cite{tomz:etal:2007,ward:etal:2013}.  Rose's basic argument is that despite longstanding arguments made by trade theorists and the World Trade Organization that WTO membership fosters greater cooperation and thereby more trade among its members, the empirics do not bear out such claims. He uses a standard gravity model with dyadic data on bilateral merchandise trade (not services) for $175$ countries over a period of five decades. Estimating this model using OLS within many differing contexts, his conclusion was that: ``An extensive search reveals little evidence that countries joining or belonging to the GATT/WTO have different trade patters from outsiders \ldots (2004, page 98, abstract).''  The data for this study have been widely used in replications by many searching for the missing effects of the WTO -- as well as preferential trade agreements, bilateral investment theories, and other aspects of modern trade theory.

When we compare the results of Rose's original OLS model to the AME model accounting for network dependencies, the results are generally similar. The main result of the model -- the null effect of membership in the WTO, as represented by the ``One-In" and ``Both-In" variables -- persists in the AME model. However, while in the original model there was a clear positive relationship between Real GDP and Trade, most of this effect vanishes in the AME model. The random effects shown in Figure~\ref{fig:roser} reveal the cause of much of this divergence. Here, the states with the most positive random effects are also states with high GDP, though not necessarily high GDP/capita.\footnote{Note: Qatar exhibits strongly negative random effects.} Thus, the effect of GDP in the original model was, in part, an artifact of first-order dependencies. Most of the other results of the model are constant across each model, though some geographic features, such as islands and landlocked states, have a more clear effect on trade once we account for these network dependencies. When we account for network interdependencies, we observe a markedly lower Root Mean Squared Error out-of-sample -- $3.23$ for the OLS model and $1.77$ for the AME model. While the basic model replicates with the basic result, there are substantial and substantive improvements gleaned from the AME results.

@@

We re-estimated model 6 from Table 6 (2017, 34). The results are presented in Figure~\ref{fig:giberrepl} in order to facilitate explicit comparison.
The results obtained with \texttt{amen} stand in stark contrast to those found with a logistic regression (with dyad clustered, robust standard errors).  Most importantly, the primary variable from the Gibler study, parity of the members of a dyad at the year in which they entered the international system, is shown to be unimportant in the AME results.  Not only is the value of this parameter small, but it has a very large relative standard error -- over a magnitude larger than the parameter itself ($z= 0.038$). In addition, the variable indicating whether both members of the dyad were coded as democracies (joint democracy) follows the same pattern: important and strong in the logistic results, but this disappears once interdependencies are modeled.  As might be expected, the strong geographic clustering in the original study is about one-quarter as strong in the AME estimations. Similarly, rivalry coefficients are about one-third the size in the AME formulation, but a great deal more precisely measured ($z=18.116$).

We utilized the original and the AME results from Gibler's model 6 in Table 6 to calculate the expected values for one scenario. We focused on the variables measuring rivalry.  We used mean or modal values for all independent variables, except we changed the rivalry variable to indicate that there was a rivalry when the actual data suggest there is none.  The expected values of this scenario are essentially a first difference plot comparing results with the model when estimated in two different ways: Gibler's GLM estimation and our AME approach.  As this Figure~\ref{fig:gibmargeff} illustrates, the AME results differ from the GLM in two distinct ways. First, the expected value of the dependent variable -- the probability of the onset of a militarized interstate dispute, is considerably higher when taking interdependencies into account with the AME model.  These are rare events, so the probabilities are low, but the difference is a factor of $3x$. Thus, you get quite substantially different expected values from these two models.  Second, the GLM model has a standard errors which underestimate the true variability, in part because some of them are assumed to be zero.  This shows up in the narrow density of predicted outcomes for the GLM model, compared to the density seen with the AME. The latter reflects a wider range of potential outcomes, reflecting the incorporation of uncertainty in the AME model.

@@

First and foremost, many  findings which emerge from models that do not take interdependencies into account lose their statistical significance when network effects are estimated via AME. This should not be news -- since the finding has long been in the theoretical literature, but given the state of current literature in international relations is still pertinent.  Not only
are coefficients biased in the OLS and logit approaches to the analysis of dyadic data, but they are often imprecisely measured, with inflated standard errors.  This means that significant testing (for better or worse) is compromised when network effects are ignored.

@@

Third, it is evident that the actual results -- not the estimated coefficents and their covariances -- which are generated by the models differ greatly in expectations.  This implies that policy experimentations with the models, as well as scenario-based simulations and forecasting of GLM models are likely to often give misleading results compared to the AME approach.

### 2017-10-21 paper/6_appendix.tex
fix rose out samp
cleanup, coefs left, waiting on rose out

% \subsection*{Additive and Multiplicative Effects Gibbs Sampler}

% To estimate, the effects of our exogenous variables and latent attributes we utilize a Bayesian probit model in which we sample from the posterior distribution of the full conditionals until convergence. Specifically, given observed data $\textbf{Y}$ and $\textbf{X}$ -- where $\textbf{X}$ is a design array that includes our sender, receiver, and dyadic covariates -- we estimate our network of binary ties using a probit framework where: $y_{ij} = 1(\theta_{ij}>0)$ and $\theta_{ij} = \bm\beta^{\top}\mathbf{X}_{ij} + a_{i} + b_{j} + \textbf{u}_{i}^{\top} \textbf{D} \textbf{v}_{j} + \epsilon_{ij}$.

% \begin{itemize}
%  \item Given initial values of $\{\bm\beta, \textbf{a}, \textbf{b}, \textbf{U}, \textbf{V}, \Sigma_{ab}, \rho, \text{ and } \sigma_{\epsilon}^{2}\}$, the algorithm proceeds as follows:
%  \begin{itemize}
%  	\item sample $\bm\theta \; | \;  \bm\beta, \textbf{X}, \bm\theta, \textbf{a}, \textbf{b}, \textbf{U}, \textbf{V}, \Sigma_{ab}, \rho, \text{ and } \sigma_{\epsilon}^{2}$ (Normal)
%  	\item sample $\bm\beta \; | \;  \textbf{X}, \bm\theta, \textbf{a}, \textbf{b}, \textbf{U}, \textbf{V}, \Sigma_{ab}, \rho, \text{ and } \sigma_{\epsilon}^{2}$ (Normal)
%  	\item sample $\textbf{a}, \textbf{b} \; | \; \bm\beta, \textbf{X}, \bm\theta, \textbf{U}, \textbf{V}, \Sigma_{ab}, \rho, \text{ and } \sigma_{\epsilon}^{2}$ (Normal)
% 	\item sample $\Sigma_{ab} \; | \; \bm\beta, \textbf{X}, \bm\theta, \textbf{a}, \textbf{b}, \textbf{U}, \textbf{V}, \rho, \text{ and } \sigma_{\epsilon}^{2}$ (Inverse-Wishart)
%  	\item update $\rho$ using a Metropolis-Hastings step with proposal $p^{*} | p  \sim$ truncated normal$_{[-1,1]}(\rho, \sigma_{\epsilon}^{2})$
%  	\item sample $\sigma_{\epsilon}^{2} \; | \; \bm\beta, \textbf{X}, \bm\theta, \textbf{a}, \textbf{b}, \textbf{U}, \textbf{V}, \Sigma_{ab}, \text{ and } \rho$ (Inverse-Gamma)
%  	\item For each $k \in K$:
%  	\begin{itemize}
%  		\item Sample $\textbf{U}_{[,k]} \; | \; \bm\beta, \textbf{X}, \bm\theta, \textbf{a}, \textbf{b}, \textbf{U}_{[,-k]}, \textbf{V}, \Sigma_{ab}, \rho, \text{ and } \sigma_{\epsilon}^{2}$ (Normal)
%  		\item Sample $\textbf{V}_{[,k]} \; | \; \bm\beta, \textbf{X}, \bm\theta, \textbf{a}, \textbf{b}, \textbf{U}, \textbf{V}_{[,-k]}, \Sigma_{ab}, \rho, \text{ and } \sigma_{\epsilon}^{2}$ (Normal)
%  		\item Sample $\textbf{D}_{[k,k]}  \; | \; \bm\beta, \textbf{X}, \bm\theta, \textbf{a}, \textbf{b}, \textbf{U}, \textbf{V}, \Sigma_{ab}, \rho, \text{ and } \sigma_{\epsilon}^{2}$ (Normal)\footnote{Subsequent to estimation, \textbf{D} matrix is absorbed into the calculation for $\textbf{V}$ as we iterate through $K$. }
%  	\end{itemize}
%  \end{itemize}
% \end{itemize}

>>>>

\subsection*{Performance Analysis}

\subsubsection*{Gibler (2017)}

\begin{figure}
	\centering   
	\subfigure[AUC]{\label{fig:giblerroc}\includegraphics[width=.45\textwidth]{gibler_roc_outSample.pdf}}
	\subfigure[Precision and Recall]{\label{fig:giblerpr}\includegraphics[width=.45\textwidth]{gibler_pr_outSample.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Gibler (2017) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

\subsubsection*{McDonald (2004)}

\begin{figure}
	\centering   
	\subfigure[AUC]{\label{fig:mcdonaldroc}\includegraphics[width=.45\textwidth]{mcdonald_roc_outSample.pdf}}
	\subfigure[Precision and Recall]{\label{fig:mcdonaldpr}\includegraphics[width=.45\textwidth]{mcdonald_pr_outSample.pdf}}
	\caption{Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

\subsubsection*{Reiter \& Stam (2003)}

\begin{figure}
	\centering   
	\subfigure[AUC]{\label{fig:reiterstamroc}\includegraphics[width=.45\textwidth]{reiter_stam_roc_outSample.pdf}}
	\subfigure[Precision and Recall]{\label{fig:reiterstampr}\includegraphics[width=.45\textwidth]{reiter_stam_pr_outSample.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

\subsubsection*{Rose (2004)}

% \begin{figure}
% 	\centering   
% 	\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=.45\textwidth]{mcdonald_roc_outSample.pdf}}
% 	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=.45\textwidth]{mcdonald_pr_outSample.pdf}}
% 	\caption{Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
% \end{figure}
% \FloatBarrier

\subsubsection*{Weeks (2012)}

\begin{figure}
	\centering   
	\subfigure[AUC]{\label{fig:weeksroc}\includegraphics[width=.45\textwidth]{weeks_roc_outSample.pdf}}
	\subfigure[Precision and Recall]{\label{fig:weekspr}\includegraphics[width=.45\textwidth]{weeks_pr_outSample.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Weeks (2012) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier
